\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-19 tex/paper.tex
save

\begin{figure*}
    \usetikzlibrary{arrows}
    \def\layersep{1cm}

@@

    \node[above] at (12.75,-2) {\small $\theta^1(f(X;\theta_f);\theta_r)$};
    \path[-o, shorten >= 0pt] (11,-2.0) edge (14,-2.0);
    \node[above] at (12.75,-3) {$\theta^2(f(X;\theta_f);\theta_r)$};
    \path[-o, shorten >= 0pt] (11,-3) edge (14,-3);
    \node[above] at (12.75,-4) {$\dots$};
    \path[-o, shorten >= 0pt] (11,-4) edge (14,-4);

@@

If $Z$ takes discrete values, then $p_{\theta_r}$ can be represented e.g. as a
probabilistic classifier $\mathbb{R} \mapsto \mathbb{R}^{|{\cal Z|}}$ whose
output $j$ (for $j=1, \dots, |{\cal Z}|$) is the estimated probability mass
$p_{\theta_r}(z_j|f(X;\theta_f))$. Similarly, if $Z$ takes continuous values and
if we assume some parameteric distribution for $Z|f(X;\theta_f)$ (e.g., a
truncated gaussian over a bounded support), then $p_{\theta_r}$ can be
represented e.g. as network whose output $j$ is the estimated value of the
corresponding parameter of that distribution (e.g., its mean and variance). As
in \citep{nix1994estimating}, the estimated probability density
$p_{\theta_r}(z|f(X;\theta_f))$ can then be evaluated for any $z \in {\cal Z}$.
As further explained in the next section, let us note that the adversary $r$ may
take any form, i.e. it does need to be a neural network, as long as it exposes a
differentiable function $p_{\theta_r}(z|f(X;\theta_f))$ of sufficient capacity
to represent the true distribution within its bounded support.

>>>>

\tikzstyle{every node}=[font=\scriptsize]
\begin{figure*}
    \usetikzlibrary{arrows}
    \def\layersep{1cm}

@@

    \node[above] at (12.75,-2) {$\theta^1(f(X;\theta_f);\theta_r)$};
    \path[-o, shorten >= 0pt] (11,-2.0) edge (14,-2.0);
    \node[above] at (12.75,-3) {$\theta^2(f(X;\theta_f);\theta_r)$};
    \path[-o, shorten >= 0pt] (11,-3) edge (14,-3);
    \node[above] at (12.75,-4) {$\dots$};
    \path[-o, shorten >= 0pt] (11,-4) edge (14,-4);

@@

If $Z$ takes discrete values, then $p_{\theta_r}$ can be represented e.g. as a
probabilistic classifier $\mathbb{R} \mapsto \mathbb{R}^{|{\cal Z|}}$ whose
output $j$ (for $j=1, \dots, |{\cal Z}|$) is the estimated probability mass
$p_{\theta_r}(z_j|f(X;\theta_f))$. Similarly, if $Z$ takes continuous values and
if we assume some parameteric distribution ${\cal D}$ for $Z|f(X;\theta_f)$ (e.g., a
truncated gaussian over a bounded support), then $p_{\theta_r}$ can be
represented e.g. as network whose output $j$ is the estimated value of the
corresponding parameter $\theta^j$ of that distribution (e.g., its mean and variance). As
in \citep{nix1994estimating}, the estimated probability density
$p_{\theta_r}(z|f(X;\theta_f))$ can then be evaluated for any $z \in {\cal Z}$.
As further explained in the next section, let us note that the adversary $r$ may
take any form, i.e. it does need to be a neural network, as long as it exposes a
differentiable function $p_{\theta_r}(z|f(X;\theta_f))$ of sufficient capacity
to represent the true distribution within its bounded support.
